---
title: "stockToolsGuide"
author: "Matthew Davis"
date: "September 18, 2017"
output: html_document
---
#### The following is a guide to stockTools


Load the symbol list and get the historical data, load to enviroment e
```{r, eval = FALSE}

data("sp500Symbols")
## build new data
e<-new.env()
failList <- getHistoricalStocks(sp500Symbols, e)
stockDataEnv<-e
save(stockDataEnv, file = 'stockDataEnv.rda')
```

#### Build a Data Frame From Stock Ticker Data 

Load pre downloaded data from and enviroment, saved as an rda file
set the dependent and class variables. 
This uses the buildStockdatasetfromEnv function to take all stocks in the enviroment, and turn them into a data data frame suitable for modeling 
```{r, cache = TRUE}
load('stockDataEnv.rda')
rd<-na.buildStockDataSetFromEnv(stockDataEnv)
## get Varible Names
classCol<- "tradeFlag" 
predVars<-colnames(rd)[!colnames(rd) %in% c( "time","tradeInd","stockName",classCol)]
dim(rd)
```

Load a pre trained cluster model for the data and use cluster prediction as features for the rd data frame

```{r}

load('clusterFit.rda') ## loads as cluster fit
rd.clean<-na.omit(rd)
km.df<-predictKmeans(clusterFit, rd.clean)
```

```

