---
title: "stockFunctions Guide"
author: "Matthew Davis"
date: "8-8-2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

##### This is a guide on how to use stockFunctions package

This package is intendent to simpify turning daily stock ticker open high low close volume data into a a matrix for machine learning.  The objective is essentailly to predict simulataniouslly a group of stocks.

get Historical stocks takes a list of stock tickers and saves them as xts objects in an Enviroment
```{r setup, comment = '', message=FALSE}
library(stockTools)
if(!exists('E'))E<-new.env()
getHistoricalStocks(c('GE',  "AA" ), e = E , startDate = '2000-01-01', endDate = '2017-08-01')
eapply(E, function(x)tail(x,1))
```

tickerEnvUpdate takes an enviroment with xts stock data, and updates each object with the latest data
```{r}
tickerEnvUpdate(E)
eapply(E, function(x)tail(x,1))
```

buildStockDataSetFromEnv takes an enviroment with xts stock ticker data stored in it and merges it together in one data frame.
It also uses functions from myfeatures.r ( a wrapper for the TTR package) to do feature engineering.

```{r}
## working here
ls(E)
head(E$AA)
x<-buildStockDataSetFromEnv(E)
dim(x)
tail(x,2)
```



